An Accurate Model for SARS-CoV-2 Pooled RT-PCR Test Errors

### 2021-09-09 paper.tex
more discussion

\section*{Introduction}
Reverse transcription polymerase chain reaction (RT-PCR) testing is a
key component in breaking transmission chains and mitigating the
COVID-19 pandemic. As such, the need for large-scale testing has
resulted in the application of techniques to increase the throughput
of RT-PCR tests \cite{DorfmanYuvalDor, PoolSize30, BayesianDorfman,
  MatrixPooling, LionDorfman}. These techniques, often termed
\emph{pooling}, or group testing, have originated in the 1940's in the
seminal work of Dorfman and his pooling technique
\cite{DorfmanOriginal, DorfmanYuvalDor}. Under Dorfman pooling, one
selects $N$ individuals and performs a single RT-PCR test on their
combined (\emph{pooled}) samples. If the pooled test yields a positive
result, then each individual is retested separately; otherwise,
everyone is declared negative. The throughput efficiency of Dorfman
pooling has been demonstrated empirically \cite{DorfmanYuvalDor} and
its error rates thoroguhly investigated \cite{Kim, Simplistic1,
  OptimalDorfmanPool}. Other commonly used techniques include
recursive pooling, wherein... Matrix pooling.. many other complex
techniques..

@@

Furthermore, an especially important
consideration in designing pooling schemes is explicitly taking the
intrinsic PCR error rates into account. As we have demonstrated above, analyzing the expected error rates of pooling schemes under a realistic probabilistic error model is readily achievable. Designing pooling schemes which optimize testing while accounting for error rates is, however, far from trivial. Nonetheless, various algorithms explicitly incorporate error rates into their pooling optimization processes (REFS), including a recent study by our group which employed the herein described error model \cite{DOPE}.

>>>>

\section*{Introduction}
Reverse transcription polymerase chain reaction (RT-PCR) testing is a
key component in breaking transmission chains and mitigating the
COVID-19 pandemic. As such, the need for large-scale testing has
resulted in the application of techniques to increase the throughput
of RT-PCR tests \cite{DorfmanYuvalDor, PoolSize30, BayesianDorfman,
  MatrixPooling, LionDorfman}. These techniques, often termed
\emph{pooling}, or group testing, have originated in the 1940's in the
seminal work of Dorfman and his pooling technique
\cite{DorfmanOriginal, DorfmanYuvalDor}. Under Dorfman pooling, one
selects $N$ individuals and performs a single RT-PCR test on their
combined (\emph{pooled}) samples. If the pooled test yields a positive
result, then each individual is retested separately; otherwise,
everyone is declared negative. The throughput efficiency of Dorfman
pooling has been demonstrated empirically \cite{DorfmanYuvalDor} and
its error rates thoroguhly investigated \cite{Kim, Simplistic1,
  OptimalDorfmanPool}. Other commonly used techniques include
recursive pooling, wherein... Matrix pooling.. many other complex
techniques.

@@

Furthermore, an especially important
consideration in designing pooling schemes is explicitly taking the
intrinsic PCR error rates into account. As we have demonstrated above, analyzing the expected error rates of pooling schemes under a realistic probabilistic error model is readily achievable. Designing pooling schemes which optimize testing while accounting for error rates is, however, far from trivial. Nonetheless, various algorithms explicitly incorporate error rates into their pooling optimization processes (REFS), including a recent study by our group which employed the herein described error model \cite{DOPE}. 
In our proposed algorithm, we have used a Bayesian experimental design criterion to create an algorithm which iteratively performs pooling schemes, updating its information based on previous results. In doing so, our pooling
scheme shows potential in terms of both reducing false-negative rates, as well as increasing
efficiency, although it has not yet been implemented in real-world
settings.
